Distributional Trees for Circular Data

### 2019-06-28 pkg/disttree/inst/IWSM2019/slides.Rnw
small touch-ups
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2627 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: f9e30d2e14d3e8de24d86a859fdee4caad228dbc

\documentclass[11pt,t,usepdftitle=false,aspectratio=43]{beamer}
\usetheme[nototalframenumber, noslidenumber]{uibk}

\title{Distributional Trees 
%and Forests \\
for Circular Data}
\author{Lisa Schlosser, Moritz N. Lang, Torsten Hothorn, \\
Georg~J.~Mayr, Reto Stauffer, Achim Zeileis}
\setbeamerfont{url}{size*={11.5pt}{13pt},series=\mdseries}
%\renewcommand{\mysize}{\fontsize{7.7pt}{9pt}\selectfont}
\URL{https://R-Forge.R-project.org/projects/partykit/ \\
https://partykit.org}
\headerimage{3}

@@

The density for $y \in [0, 2\pi)$ is given by:
$$
f_\mathrm{vM}(y; \mu, \kappa) = \frac{1}{2 \pi I_0(\kappa)}~e^{ \kappa \cos(y - \mu)}\label{schlosser:equ_vm}
$$
where $I_0(\kappa)$ is the modified Bessel function of the first kind and order $0$.

@@

\small{\url{https://R-Forge.R-project.org/projects/partykit/}\\ 
and\\
\url{https://r-forge.r-project.org/projects/uibk-rprog-2018/}}\\

@@

\begin{frame}
\frametitle{References (1)}

@@

\begin{frame}
\frametitle{References (2)}

>>>>

\documentclass[11pt,t,usepdftitle=false,aspectratio=43]{beamer}
\usetheme[url, license]{uibk}

\title{Distributional Trees 
%and Forests \\
for Circular Data}
\author{Lisa Schlosser, Moritz N. Lang, Torsten~Hothorn,\\
Georg~J.~Mayr, Reto Stauffer, Achim Zeileis}
\setbeamerfont{url}{size*={11.5pt}{13pt},series=\mdseries}
%\renewcommand{\mysize}{\fontsize{7.7pt}{9pt}\selectfont}
\URL{https://R-Forge.R-project.org/projects/partykit/}
\headerimage{3}

@@

The density for $y \in [0, 2\pi)$ is given by:
$$
f_\text{vM}(y; \mu, \kappa) = \frac{1}{2 \pi I_0(\kappa)}~e^{ \kappa \cos(y - \mu)}\label{schlosser:equ_vm}
$$
where $I_0(\kappa)$ is the modified Bessel function of the first kind and order $0$.

@@

\small{\url{https://R-Forge.R-project.org/projects/partykit/}\\ 
and\\
\url{https://R-Forge.R-project.org/projects/uibk-rprog-2018/}}\\

@@

\begin{frame}
\frametitle{References}

@@

\begin{frame}
\frametitle{References}
